The Concurrent Calculi Formalisation Benchmark

### 2023-10-12 paper/paper.tex
fixed a comment in the further challenge section

Some interesting aspects of message passing calculi to explore in further
challenges could be multiparty session types, and choreographies because their
definitions and meta-theory have aspects that we do not cover here\fxerror{Such
as?} (although the aspects that we cover here do appear in these problems).
Also, one could easily design a challenge that goes beyond our coinduction
challenge, by exploring different notions of bisimilarity (barbed, or weak,
etc.), and trace equivalence.

>>>>

Some interesting aspects of message passing calculi to explore in
further challenges could be multiparty session types, and
choreographies because their definitions and meta-theory have aspects
that we do not cover here (e.g.: representing well formed global types
and projection as a partial function). Although, dually, some aspects
that we cover here do appear in these problems. Also, one could easily
design a challenge that goes beyond our coinduction challenge, by
exploring different notions of bisimilarity (barbed, or weak, etc.),
and trace equivalence.
